---
title: "Exercise 3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Amanda Winata (12361231)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Martrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to it's bullet point or use a new level 3 heading if you want.
-   Always render the R code for your solutions and make sure to include
    the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown document. Submit the files separately on moodle, **not**
    as a zip archive.

## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  Start by initializing a new R project with git support, called
    `2024-exeRcise-sheet-3`. If you forgot how to do this, you can
    follow this
    [guide](https://malikaihle.github.io/Introduction-RStudio-Git-GitHub/rstudio_project.html).
b)  Commit the files generated by Rstudio.
c)  For all of the following tasks in this exercise sheet we ask you to
    always commit your changes after finishing each subtask e.g. create
    a commit after task *1d*, *1e* etc.

> Note: This applies only to answers that have text or code as their
> answer. If you complete tasks in a different order or forget to commit
> one, this is no problem. If you change your answers you can just
> create multiple commits to track the changes.

d)  Name 2 strengths and 2 weaknesses of git. (Don't forget to create a
    commit after this answer, see *1c*)
    
**Strengths:**

1. **Version Control:** Git enables tracking changes and reverting to previous states, simplifying version control and making development more efficient.

2. **Collaboration:** Git supports multiple users on the same project, providing tools for merging changes and resolving conflicts, enabling effective teamwork.

**Weaknesses:**

1. **Complexity:** Git can be difficult to learn and use, especially for beginners. Understanding the numerous commands and options, and concepts such as branching, merging, and rebasing can be overwhelming and tricky.

2. **Repository Size Limitations:** GitHub recommends keeping repositories under 1 GB for optimal performance, making the management of large repositories challenging.

e)  Knit this exercise sheet. Some new files will automatically be
    generated when knitting the sheet e.g. the HTML page. Ignore these
    files, as we only want to track the source files themselves.

## Exercise 2: Putting your Repository on GitHub (3.5 Points)

For this task you will upload your solution to GitHub.

a)  Create a new repository on GitHub in your account named
    `exeRcise-sheet-3`. Make sure you create a **public repository** so
    we are able to see it for grading. Add the link to the repository
    below:
    
Link to the repository: <https://github.com/wntamanda/exeRcise-sheet-3.git>

b)  Push your code to this new repository by copying and executing the
    snippet on github listed under
    `…or push an existing repository from the command line`.
c)  Regularly push your latest changes to GitHub again and especially do
    so when you are finished with this sheet.

## Exercise 3: Baby-Names in Munich (3.5 Points)

Download the latest open datasets on given names ("Vornamen") from the
open data repository of the city of Munich for the years `2023` and
`2022`.

Link: <https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen>

a)  Download the data for both years and track it in git. For small
    datasets like these adding them to git is not a problem.

b)  Load the data for both years into R. Check the type of the count
    variable ("Anzahl") and look into the data to determine why it is
    not numeric? Fix the problem in an appropriate manner, it is OK if
    some of the counts are inaccurate because of this. Explain your
    solution and the repercussions.
    
    ```{r task3b}
    library(dplyr)
    library(readr)
    
    data_2023 <- read_csv("vornamen-muenchen-2023.csv")
    data_2022 <- read_csv("open_data_portal_2022.csv")
    
    # Checking the datatype of the 'Anzahl' variable
    str(data_2023$Anzahl)
    str(data_2022$Anzahl)
    
    data_2023 <- data_2023 %>%
      mutate(Anzahl = as.numeric(gsub("[^0-9]", "", Anzahl)))
    
    data_2022 <- data_2022 %>%
      mutate(Anzahl = as.numeric(gsub("[^0-9]", "", Anzahl)))
    
    # Checking the datatype of the 'Anzahl' variable after conversion
    str(data_2023$Anzahl)
    str(data_2022$Anzahl)
    
    # Checking for NA values in 'Anzahl' after conversion
    sum(is.na(data_2023$Anzahl))
    sum(is.na(data_2022$Anzahl))
    ```

**Explanation :** The `Anzahl` column was cleaned by using `gsub("[^0-9]", "", Anzahl)` to remove any non-numeric characters and then converting the cleaned strings to numbers with `as.numeric()`. This makes the `Anzahl` column numeric and ready for calculations. However, this method can introduce errors, such as turning ranges into a single numeric value. This approach cleans the data but can sometimes misinterpret the values.

c)  Calculate the total number of babies born in Munich in 2022
    and 2023. Which year had the bigger baby-boom?
    
    ```{r task3c}
    babytotal_2023 <- sum(data_2023$Anzahl, na.rm = TRUE)
    babytotal_2022 <- sum(data_2022$Anzahl, na.rm = TRUE)
    
    print(babytotal_2023)
    print(babytotal_2022)
    ```

**Year :** 2022 had the bigger baby-boom.

d)  Add a new column `year` to both datasets which holds the correct
    year for each.
    
    ```{r task3d }
    data_2023 <- data_2023 %>%
      mutate(year = 2023)
  
    data_2022 <- data_2022 %>%
      mutate(year = 2022)
        
    # To check if the 'year' column is successfully created
    colnames(data_2023)
    colnames(data_2022)
    ```

e)  Combine both datasets into one using `bind_rows()`.

    ```{r task3e}
    combined_data <- bind_rows(data_2023, data_2022)
    ```

f)  Combine the counts for same names to determine the most popular
    names across both years. Print out the top 10 names in a nicely
    formatted table for both years. Include a table caption.
    
    ```{r task3f, results='asis'}
    library(knitr)
    
    most_popular_names <- combined_data %>%
      group_by(Vorname) %>%
      summarize(Total = sum(Anzahl, na.rm = TRUE)) %>%
      arrange(desc(Total)) %>%
      slice_head(n = 10)
    
    kable(most_popular_names, caption = "Top 10 Most Popular Baby Names in Munich (2022-2023)")
    ```

## Exercise 4: Open Analysis (4 points)

This exercise is a bit more open-ended. You can choose any dataset from
[Our World in Data](https://ourworldindata.org/) and analyze it, while
determining the research question yourself.

a)  Go to <https://github.com/owid/owid-datasets/tree/master/datasets>
    and choose a dataset that interests you. You can have a look at
    <https://ourworldindata.org/> to gather some inspiration.
b)  Download the dataset and track it in git.
c)  Put the name / title of the dataset and a link to it below.

-   Dataset Name: Suicide rates by sex and age (IHME, 2019).csv
-   Link: <https://github.com/owid/owid-datasets/blob/master/datasets/Suicide%20rates%20by%20sex%20and%20age%20(IHME%2C%202019)/Suicide%20rates%20by%20sex%20and%20age%20(IHME%2C%202019).csv>

d)  Come up with a (research) question you want to answer with the data
    and briefly explain why you believe this is an interesting question
    within one sentence. It should be a question that can be answered
    with the dataset and using R.
    
**Question: ** Which age group and gender have the highest suicide rates in Germany, and how have these rates changed over time?

e)  Use R to answer your chosen question.
f)  Create a meaningful plot / figure with the dataset. Make sure to
    provide a figure caption (via the chunk options / Rmarkdown) and
    correctly label the figure.

## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.
